---
title: "5361 stat Homework1"
author: "Qi&Weixing"
date: "January 26, 2018"
output:
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
t <- c(0.0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72)
n <- c(10^2, 10^3, 10^4)

###Function with the true value of cdf
phi_true <- function(t){
  x <- array()
  for (i in 1:length(t)){
    x[i] <- pnorm(t[i])
  } 
  return(x)
}

###Function with the approximation at a = 10^2, 10^3, 10^4
phi_est <- function(n, t) {
  m <- array(0, dim = c(9,3))
  for (k in 1:length(n)) {
    A <- rnorm(n[k])
    for (i in 1:length(t)) {
      for (j in 1:length(A)) {
        if (A[j] <= t[i]) I <- 1
        else I <- 0
      m[i,k] <- (m[i,k]+I)
      }
    m[i,k] <- m[i,k]/length(A)
    }
  }
  return(m)
}

###Function with the combination the True value and Estimated value
comparison_val <- function(n, t){
  cbind(phi_est(n,t), phi_true(t))
}

###Function with the experiments of 100 times
experiment_100 <- function(t,n){
  x <- array(0, dim = c(9,4,100))
  for (i in 1:100){
    a <- comparison_val(n, t)
    for (j in 1:length(t)){
      for (k in 1:(length(n)+1)){
        x[j,k,i] <- a[j,k]
      }
    }
  }
  return(x)
}

###Box Plot of the bias at all t
#boxplot(experiment_100(t,n)[ , 1, ]~t)
#boxplot(experiment_100(t,n)[ , 2, ]~t)
#boxplot(experiment_100(t,n)[ , 3, ]~t)

```

## Abstract

First, we use built-in function pnorm to calculate the true value of CDF equation (1). Then we use the (2) equation to calculate the estimated value. In the process of using (2), we generate different amounts of numbers and calculate value in different time. Finally we uotput our table and boxplots.

## Math equations
\begin{equation}
\Phi(t) = \int_{-\infty}^t \frac{1}{\sqrt{2\pi}} e^{-y^2 / 2} dy,
\tag{1}
\end{equation}

\begin{equation}
\hat\Phi(t) = \frac{1}{n} \sum_{i=1}^n I(X_i \le t),
\tag{2}
\end{equation}
```{r true_value}
phi_true
```
```{r experiment_value}
phi_est
```
```{r experiment_100}
experiment_100
```
```{r compare}
comparison_val
```
## Included Plots and Tables
We also generate plots and tables;

```{r pressure, echo=FALSE}
###Box Plot of the bias at all t
boxplot(experiment_100(t,n)[ , 1, ]~t)
boxplot(experiment_100(t,n)[ , 2, ]~t)
boxplot(experiment_100(t,n)[ , 3, ]~t)
print(experiment_100(t,n)[ , ,1])
```
We omit the rest of tables.


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
